Landau quantization of nearly degenerate bands, \\ and full symmetry classification of avoided Landau-level crossings

### 2019-04-06 paper.tex
Updates from Overleaf

\begin{figure}
\includegraphics[width=1.0\columnwidth]{error.png}
\caption{{Comparison of quantization rule and exact diagonalization. (a) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model, we plot in left panel $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that lies closest to energy $E=0.4eV$, where $\epsilon_\text{rule}$ is determined by Eq. (\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RD}(\bK)$ plus the Zeeman coupling to spin. We also plot in right panel $l^2\delta S^2/S$, which has a strong positive correlation with the error. (b) For various parametrizations ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in the left panel the error for a single Landau level that is closest to $\epsilon_0$ [as defined in Eq. (\ref{whereisdiracpoint})] $\epsilon_\text{rule}$ is determined by Eq. (\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RZ}(\bK)$ plus the Zeeman coupling to spin. The corresponding $l^2 \delta S^2/S$ is plotted in the right panel. For numerical convergence\cite{RZfignote}, we have presented data only in a strip [within ($\alpha$, $Z_\parallel$)-space] where $0.4{<}\epsilon_0{<}1.0$(eV).Parameters for (a): $m=0.076m_0$, $l=200$\AA~and $g_{s\perp}=2$; parameters for (d): $m=0.076m_0$, $l=100$\AA~and $g_{s\perp}=2$.}\label{fig:error}}
\end{figure}

@@

\begin{table*}[t]
\begin{tabular*}{2\columnwidth}{c@{\extracolsep{\fill}}ccccccc}
\hlineB{2}
class label & $u$ & $s$ & symmetry constraint & $\det{\A}$ & $\breve{g}$ & codimension \\
\hline
I-1 & 0 & 0 & $\A=\breve{g}\A\breve{g}^{-1}$ & - & $\breve{g}\propto I$ & 3  \\
&  &  &  & - & $\breve{g} \not\propto I$ & 1  \\
I-2 & 0 & 1 & $\A=\breve{g}\A^*\breve{g}^{-1}$ & 1 & $(\breve{g}K)^2=I$ & 1 \\
&  &  &  & 1 & $(\breve{g}K)^2=-I$ & 3 \\
&  &  &  & -1 & $(\breve{g}K)^2=I$ & $\infty$ \\
&  &  &  & -1 & $(\breve{g}K)^2=-I$ & $\times$ \\
II-1 & 0 & 0 & $\A=\breve{g}(g^{L-1}\circ\bk_0) \A_{1/L}^{L}$ & - & - & 1 \\
II-2 & 1 & 1 & $\A=\breve{g}\A^T\breve{g}^{-1}$ & - & $(\breve{g}K)^2=I$ & 2 \\
& & & & - & $(\breve{g}K)^2\ne I$ & 0 \\
II-3 & 0 & 1 & $\A=\breve{g}(g^{L-1}\circ\bk_0) (K^i\A_{1/L}K^i)^L$ & - & $L=N$ & 1 \\
& & & & 1 & $L\ne N$ & 1 \\
& & & & -1 & $L\ne N$, $(\breve{g}K)^2=I$ & $\infty$ \\
& & & & -1 & $L\ne N$, $(\breve{g}K)^2=-I$ & $\times$ \\
II-4 & 1 & 0 & $\A=\breve{g}\A^\dagger\breve{g}^{-1}$ & 1 &$\breve{g} \propto \sigma_z$& 2\\
& & & & 1 &$\breve{g} \not\propto \sigma_z$ & 0\\
& & & & -1 &$\breve{g} \propto I$ & 2\\
& & & & -1 &$\breve{g} \not\propto I$& 0\\
III-1 & 0 & 0 & $\A_2=\breve{g}\A_1\breve{g}^{-1}$ & - & - & 3 \\
III-2 & 1 & 1 & $\A_2=\breve{g}\A_1^T\breve{g}^{-1}$ & - & - & 3 & \\
III-3 & 0 & 1 & $\A_2=\breve{g}\A_1^*\breve{g}^{-1}$ & - & - & 3\\
III-4 & 1 & 0 & $\A_2=\breve{g}\A_1^\dagger\breve{g}^{-1}$ & - & - & 3\\
\hlineB{2}
\end{tabular*}
\caption{Codimensions of degeneracy manifold of $\A$ under constraints of different type of symmetries. Most of the symmetry constraints on $\A$ are reproduced from Ref. \onlinecite{100p} except for class II-1 and II-3, where a special gauge is chosen. $\infty$ in the codimension column denotes that eigenvalues of $\A$ cannot be degenerate; $\times$ denotes an entry where we cannot self-consistently impose the symmetry constraint and the conditions on det$\A$ and $\breve{g}$ for a two-by-two unitary $\A$. In the second to last column, $\breve{g}$ is either chosen to be diagonal or off-diagonal.\label{table:fullcodimension}}
\end{table*}

>>>>

\begin{figure}
\includegraphics[width=1.0\columnwidth]{error.png}
\caption{{Comparison of quantization rule and exact diagonalization. (a) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model, we plot in left panel $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that lies closest to energy $E=0.4eV$, where $\epsilon_\text{rule}$ is determined by Eq. (\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RD}(\bK)$ plus the Zeeman coupling to spin. We also plot in right panel $l^2\delta S^2/S$, which has a strong positive correlation with the error. (b) For various parametrizations ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in the left panel the error for a single Landau level that is closest to $\epsilon_0$ [as defined in Eq. (\ref{whereisdiracpoint})] $\epsilon_\text{rule}$ is determined by Eq. (\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RZ}(\bK)$ plus the Zeeman coupling to spin. The corresponding $l^2 \delta S^2/S$ is plotted in the right panel. For numerical convergence\cite{RZfignote}, we have presented data only in a strip [within ($\alpha$, $Z_\parallel$)-space] where $0.4{<}\epsilon_0{<}1.0$(eV).Parameters for (a): $m=0.076m_0$, $l=200$\AA~and $g_{s\perp}=2$; parameters for (b): $m=0.076m_0$, $l=100$\AA~and $g_{s\perp}=2$.}\label{fig:error}}
\end{figure}

@@

\begin{table*}[t]
\begin{tabular*}{2\columnwidth}{c@{\extracolsep{\fill}}cccccc}
\hlineB{2}
class label & $u$ & $s$ & symmetry constraint & $\det{\A}$ & $\breve{g}$ & codimension \\
\hline
I-1 & 0 & 0 & $\A=\breve{g}\A\breve{g}^{-1}$ & - & $\breve{g}\propto I$ & 3  \\
&  &  &  & - & $\breve{g} \not\propto I$ & 1  \\
I-2 & 0 & 1 & $\A=\breve{g}\A^*\breve{g}^{-1}$ & 1 & $(\breve{g}K)^2=I$ & 1 \\
&  &  &  & 1 & $(\breve{g}K)^2=-I$ & 3 \\
&  &  &  & -1 & $(\breve{g}K)^2=I$ & $\infty$ \\
&  &  &  & -1 & $(\breve{g}K)^2=-I$ & $\times$ \\
II-1 & 0 & 0 & $\A=\breve{g}(g^{L-1}\circ\bk_0) \A_{1/L}^{L}$ & - & - & 1 \\
II-2 & 1 & 1 & $\A=\breve{g}\A^T\breve{g}^{-1}$ & - & $(\breve{g}K)^2=I$ & 2 \\
& & & & - & $(\breve{g}K)^2\ne I$ & 0 \\
II-3 & 0 & 1 & $\A=\breve{g}(g^{L-1}\circ\bk_0) (K^i\A_{1/L}K^i)^L$ & - & $L=N$ & 1 \\
& & & & 1 & $L\ne N$ & 1 \\
& & & & -1 & $L\ne N$, $(\breve{g}K)^2=I$ & $\infty$ \\
& & & & -1 & $L\ne N$, $(\breve{g}K)^2=-I$ & $\times$ \\
II-4 & 1 & 0 & $\A=\breve{g}\A^\dagger\breve{g}^{-1}$ & 1 &$\breve{g} \propto \sigma_z$& 2\\
& & & & 1 &$\breve{g} \not\propto \sigma_z$ & 0\\
& & & & -1 &$\breve{g} \propto I$ & 2\\
& & & & -1 &$\breve{g} \not\propto I$& 0\\
III-1 & 0 & 0 & $\A_2=\breve{g}\A_1\breve{g}^{-1}$ & - & - & 3 \\
III-2 & 1 & 1 & $\A_2=\breve{g}\A_1^T\breve{g}^{-1}$ & - & - & 3 \\
III-3 & 0 & 1 & $\A_2=\breve{g}\A_1^*\breve{g}^{-1}$ & - & - & 3\\
III-4 & 1 & 0 & $\A_2=\breve{g}\A_1^\dagger\breve{g}^{-1}$ & - & - & 3\\
\hlineB{2}
\end{tabular*}
\caption{Codimensions of degeneracy manifold of $\A$ under constraints of different type of symmetries. Most of the symmetry constraints on $\A$ are reproduced from Ref. \onlinecite{100p} except for class II-1 and II-3, where a special gauge is chosen. $\infty$ in the codimension column denotes that eigenvalues of $\A$ cannot be degenerate; $\times$ denotes an entry where we cannot self-consistently impose the symmetry constraint and the conditions on det$\A$ and $\breve{g}$ for a two-by-two unitary $\A$. In the second to last column, $\breve{g}$ is either chosen to be diagonal or off-diagonal.\label{table:fullcodimension}}
\end{table*}
